### 2016-09-15 GPCE2016/sections/Introduction.tex
revisions

Regardeless of the OO model, inheritance is a key mechanism is OO 
languages. Inheritance provides a modularization mechanism, which 
is used to reuse implementations from inherited classes/objects. 
Unfortunatelly, as widely acknowledged in the literature~\cite{scharli03traits,Sak89dis,bracha90mixin,malayeri2009cz}
multiple inheritance, especially when combined with state, has several
tricky issues, including several variants of the famous 
\emph{diamond problem}~\cite{}. Many of the problems related to 
inheritance arize from the direct use of \emph{fields} to model state. 
Inheriting two fields of the same name raises 
the question of whether the two fields should be kept, or only one 
field should exists (and if so, which value should be picked). Initialization 
of the fields is also problematic, since initialization code may be inherited from 
multiple parents. Finally, an additional problem with mutable fields is that their 
type cannot be type-refined in extensions, which can cause modularity problems
~\cite{wadler98expression,eptrivially}.

>>>>

Regardeless of the OO model, inheritance is a key mechanism is OO 
languages. Inheritance provides a modularization mechanism, which 
is used to reuse implementations from inherited classes/objects. 
Unfortunatelly, as widely acknowledged in the literature~\cite{scharli03traits,Sak89dis,bracha90mixin,malayeri2009cz}
multiple inheritance, especially when combined with state, has several
tricky issues, including several variants of the famous 
\emph{diamond problem}~\cite{bracha90mixin,Sak89dis}. Many of the problems related to 
inheritance arize from the direct use of \emph{fields} to model state. 
Inheriting two fields of the same name raises 
the question of whether the two fields should be kept, or only one 
field should exist (and if so, which value should be picked). Initialization 
of the fields is also problematic, since initialization code may be inherited from 
multiple parents. Finally, an additional problem with mutable fields is that their 
type cannot be type-refined in extensions, which can cause modularity problems
~\cite{wadler98expression,eptrivially}.
